Notes

### 2020-03-29 Notes/Notes.tex
add unit conversion discussion in notes

>>>>

\subsection{unit conversion}

So this part is typed up just to fix units and $2\pi$ not for correct math, please check if this makes sense...

We have time $t \in [0,T]$ where $T=N_T \times 10^{-6} sec$ is annealing time with unit of micro sec. $N_T$ is just dimensionless number. The time is mapped to the dimensionless schedule $s\in [0,1]$ through $s=t/T$.

Now the equation we are solving is
\begin{equation}
 i \hbar \frac{d}{dt}\psi = H \psi .
\end{equation}

The Hamiltonian is $H=N_H \times GHz \times h =N_H \times 10^9  \times h/( sec)$ where $N_H$ is the dimensionless numerical value. Use
\begin{equation}
\frac{d}{dt}\psi = \frac{d}{Tds}\psi .
\end{equation}
So the equation is
\begin{align}
  \frac{d}{ds}\psi  &=  -i \frac{H\times T}{\hbar} \psi  &\\
   &=  -i \frac{N_H \times 10^9 \times h \times N_T \times 10^{-6} sec \times 2\pi }{h\times sec  } \psi &  \\
  &= -i N_H \times N_T \times 10^{3} \times (2\pi) \psi  &.
\end{align}
and this is why the factor $10^{3} \times (2\pi)$.
